iterSim

### 2022-12-15 analyses/SIMpaperResultscopy/complexSim.Rmd
re-analyzed

  ######################
  ###DeepSurv
  ######################
  coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
                  num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = F,
                  learning_rate = 0.001,lr_decay=10^-7)
  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))

  ######################
  ###Deephit
  ######################
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  hitnnSurv<-t(hitnnSurv)
  colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

@@

>>>>

  ######################
  ###DeepSurv
  ######################
  coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
                  num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = F,
                  learning_rate = 0.001,lr_decay=10^-7)
  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  #colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))

  ######################
  ###Deephit
  ######################
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  hitnnSurv<-t(hitnnSurv)
  #colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

@@

ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()

### 2022-12-15 analyses/SIMpaperResultscopy/simpleSim.Rmd
re-analyzed

easysim<-F
hardsim<-T
numSamp<-2000
```

@@

pos<-1
for(iter in 1:iteration){

@@

  ##########################
  ###Split data
  ##########################
  samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  data<-data[,-1]
  data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data[samp,]
  test<-data[-samp,-c(ncol(data))]
  fullTest<-data[-samp,,drop=F]
  times<-seq(from=0,
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

@@

    dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo)
    py_run_string("del dsmfitter")
    rm(dsmfitter)
    iteration<-iteration+1
    next
  }
  colnames(dsmSurv) <-seq(0.01,1,by=0.01)
  dsmSurvProper<-pyProcess(dsmSurv,times=times)
  colnames(dsmSurvProper) <-seq(0,1,length.out = ncol(dsmSurvProper))
  py_run_string("del dsmfitter")
  rm(dsmfitter)

@@

  class(annProperpoly)<-c("tunnel",class(annProperpoly)) 
  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly,
                                  'dsm'=dsmSurvProper) ,#'dsm'=dsmCleaned,
                                  data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score
  ########################
  ###C-Index
  ########################
  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -15)
  tempTims<-tail(tempTims, -10)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=9)
  et_train<-as.matrix(train)#[,c(5,4)]
  et_test<-as.matrix(fullTest[,c(5,4)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','Optimal','PMNN_Poly','dsm')
  cScoreTemp[,1]<- tempTims

  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 annProperpoly
  )

  cScore[[pos]]<-cIndexSummary(et_train=et_train
                               , et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )

  saveRDS(BrierIPAList,'100easyBrier.rds')
  saveRDS(cScore,'100easycidx.rds')
  pos<-pos+1
}

end_time <- Sys.time()

@@

```{r complexPrep,eval=hardsim}

##############################
###set up complex simulation
##############################

# Define a function returning the log cum hazard at time t
logcumhaz <- function(t, x, betas, knots) {

  # Obtain the basis terms for the spline-based log
  # cumulative hazard (evaluated at time t)
  basis <- flexsurv::basis(knots, log(t))

  # Evaluate the log cumulative hazard under the
  # Royston and Parmar specification
  res <-betas[["gamma0"]] * basis[[1]] + 
    betas[["gamma1"]] * basis[[2]] +
    betas[["gamma2"]] * basis[[3]] +
    betas[["gamma3"]] * basis[[4]] +
    betas[["gamma4"]] * basis[[5]] +
    betas[["z1"]] * x[["z1"]]+
    betas[["z2"]] * x[["z2"]]+
    betas[["z3"]] * x[["z3"]]+
    betas[["term1"]] * x[["z1"]]*x[["z2"]]*t+
    betas[["term2"]] * x[["z1"]]*x[["z3"]]+
    betas[["term3"]] * x[["z2"]]*(x[["z3"]])
  #
  # Return the log cumulative hazard at time t
  res
}
url<-'app.txt'
ds <- read.table(url, sep = '',header = TRUE)
ds$years.at.risk=pmin(ds$agein80,ds$onset)
brcancer$rectime<-brcancer$rectime/max(brcancer$rectime)
true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1, data = brcancer, k = 3) #from flexsurv

# Simulate the event times
coefficients<-true_mod$coefficients
coefficients<-c(coefficients,z1=1,z2=1,z3=1,term1=10,term2=2,term3=2)

```{r totalSim,eval=hardsim}

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()
pos<-1
for(iter in 1:iteration){

  #########################
  ###Simulate date
  #########################
  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5)))
  true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                       data = brcancer, k = 3
  ) #from flexsurv
  dat <- simsurv(betas = coefficients, # "true" parameter values
                 x = cov,                   # covariate data for 200 individuals
                 knots = true_mod$knots,    # knot locations for splines
                 logcumhazard = logcumhaz,  # definition of log cum hazard
                 maxt = 1,               # no right-censoring
                 interval = c(0,10000000)) # interval for root finding
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)

  #########################
  ###Simulate data
  #########################
  samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  data<-data[,-1]
  data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data[samp,]
  test<-data[-samp,-c(ncol(data))]
  fullTest<-data[-samp,,drop=F]
  times<-seq(from=0,
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

  ###########################
  ###casebase optimal model
  ###########################
  final_mod_cb_glm <- fitSmoothHazard(status~bs(time)-time+z1+z2+z3+z1:z2:time+z1:z3+z2:z3,
                                      data = train,
                                      time = "time",
                                      event="status",
                                      ratio = 100
  )

  summary(final_mod_cb_glm)
  tglmAbsRisk<-absoluteRisk(final_mod_cb_glm,time=times,newdata=test,type="CI")
  tglmAbsRisk<-as.data.frame(tglmAbsRisk)
  rownames(tglmAbsRisk)<-tglmAbsRisk$time
  trueGlmProper<- t(tglmAbsRisk[-1,-1])
  class(trueGlmProper)<-c("tunnel",class(trueGlmProper))

  #########################
  ###casebase+splines
  #########################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

  glmAbsRisk<-absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI")

  glmAbsRisk<-as.data.frame(glmAbsRisk)

  rownames(glmAbsRisk)<-glmAbsRisk$time
  glmProper<- t(glmAbsRisk[-1,-1])

  class(glmProper)<-c("tunnel",class(glmProper))

  ######################
  ###PMNN splines
  ######################
  covars_input<-layer_input(shape=c(length(colnames(mod_cb_glm$data))-2+3),
                            name = 'main_input'
  )
  covars_output<-covars_input%>% #layer_batch_normalization()%>%
    layer_dense(units=layer1,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer2,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer3,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=layer4,use_bias = T,activation = 'relu')%>%
    layer_dropout(drpt)%>%
    layer_dense(units=1,use_bias = T)

  ######################
  ###DeepSurv
  ######################
  coxnn<-deepsurv(Surv(time, status) ~ .,data = train, frac = 0.2, activation = "relu",
                  num_nodes = c(layer1,layer2,layer3,layer4), dropout = drpt,
                  early_stopping = TRUE, epochs = epo,
                  batch_size = bsize,device = "cpu",best_weights=T,
                  patience = patience,min_delta=min_delta,batch_norm = F,
                  learning_rate = 0.001,lr_decay=10^-7)
  coxnnsurv<- predict(coxnn,newdata = test,type="survival")
  colnames(coxnnsurv)<-seq(0,1,length.out = ncol(coxnnsurv))
  cnnCleaned<-pyProcess(coxnnsurv,times=times)
  colnames(cnnCleaned)<-seq(0,1,length.out = ncol(cnnCleaned))

  ######################
  ###Deephit
  ######################
  source_python('src/deephitter.py')
  hitnnSurv=fitDeephit(train,fullTest,bsize,epo,patience=patience,min_delta=min_delta,drpt=drpt)
  hitnnSurv<-t(hitnnSurv)
  colnames(hitnnSurv)<-seq(0,1,length.out = ncol(hitnnSurv))
  deephitCleaned<-pyProcess(hitnnSurv,times=times)
  colnames(deephitCleaned)<-seq(0,1,length.out = ncol(deephitCleaned))
  py_run_string("del fitDeephit")
  rm(fitDeephit)

  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly),
                             #'dsm'=dsmSurvProper) ,#'dsm'=dsmCleaned,
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

  ######################
  ###C-Index
  ######################
  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -15)
  tempTims<-tail(tempTims, -10)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=8)
  et_train<-as.matrix(train)#[,c(5,4)]
  et_test<-as.matrix(fullTest[,c(5,4)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','Optimal','PMNN_Poly')#,'dsm')
  cScoreTemp[,1]<- tempTims
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))
  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 annProperpoly
  )

  cScore[[pos]]<-cIndexSummary(et_train=et_train
                               , et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )

  saveRDS(BrierIPAList,'results/100hardBrier.rds')
  saveRDS(cScore,'results/100hardcidx.rds')
  pos<-pos+1
}

>>>>

easysim<-T
numSamp<-2000
```

@@

pos<-1

while (pos <= iteration) {

@@

  ##########################
  ###Split data
  ##########################
  samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  data<-data[,-1]
  data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data[samp,]
  test<-data[-samp,-c(ncol(data))]
  fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

@@

    dsmSurv<-dsmfitter(train=train,fullTest=fullTest,bsize=bsize,epochs=epo)
    py_run_string("del dsmfitter")
    rm(dsmfitter)
    next
  }
  colnames(dsmSurv) <-seq(0.01,1,by=0.01)
  dsmSurvProper<-pyProcess(dsmSurv,times=times)
  colnames(dsmSurvProper) <-seq(0,1,length.out = ncol(dsmSurvProper))
  py_run_string("del dsmfitter")
  rm(dsmfitter)

@@

  class(annProperpoly)<-c("tunnel",class(annProperpoly)) 
  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly,
                                  'dsm'=dsmSurvProper) ,#'dsm'=dsmCleaned,
                                  data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

  #######################
  ###Cox 
  ######################
  a<-survfit(cox, newdata=fullTest,times=times)
  rownames(a$surv)<-a$time
  coxlinSurv<-pyProcess(t(a$surv),times=times)
  colnames(coxlinSurv)<-seq(0,1,length.out = ncol(coxlinSurv))

  ######################
  ###C-Index
  ######################

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 trueGlmProper,
                 annProperpoly,
                 dsmSurvProper
  )

  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(train)[,c(5,4)]
  et_test<-as.matrix(fullTest[,c(5,4)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','Optimal','PMNN_Poly','dsm')#,'dsm')
  cScoreTemp[,1]<- tempTims

  cScore[[pos]]<-cIndexSummary(et_train=et_train,
                               et_test=et_test,
                               riskList=riskList,
                               cScore=cScoreTemp
  )

  saveRDS(BrierIPAList,'results/100easyBrier.rds')
  saveRDS(cScore,'results/100easycidx.rds')
  pos<-pos+1
}
end_time <- Sys.time()

@@
